The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-15 analysis/paper/paper.qmd
Update function names for top words

```{r}
# Which are the top n most frequently used words in each thesis?
top_n_word_count_per_document(data = emu_theses_words, 
                              top_n = 3, 
                              title_col = "title", 
                              word_col = "word")
```

```{r}
# Which are the top n most frequently used words in all theses`?
top_n_word_count_per_corpus(data = emu_theses_words, 
                            top_n = 5, 
                            word_col = "word")
```

>>>>

```{r}
# Which are the top n most frequently used words in each thesis?
get_top_words_per_document(data = emu_theses_words, 
                           top_n = 3, 
                           title_col = "title", 
                           word_col = "word")
```

```{r}
# Which are the top n most frequently used words in all theses`?
get_top_words_per_corpus(data = emu_theses_words, 
                         top_n = 5, 
                         word_col = "word")
```
